Graphical representation example: Alternative interpretations

### 2023-11-15 notebooks/Graphical_representation_alternatives.Rmd
Formats output with table of contents and section headers

---
title: 'Graphical representation example: Alternative interpretations'
output:
  html_document:
    df_print: paged
    code_folding: hide
---

@@

@@

@@

```{r item-plot-out}
#| fig.cap: Item plots in an oblique test space.
plot_oblique
```

@@

@@

```{r}
variances  <- c(2, 1.5)
sd_matrix  <- variances |> sqrt() |> diag()
cov_matrix <- sd_matrix %*% corr_matrix %*% sd_matrix
```

@@

```{r}
# Oblique case:

>>>>

---
title: 'Graphical representation example: Alternative interpretations'
output:
  html_document: 
    df_print:        paged
    code_folding:    hide
    toc:             yes
    toc_float:       yes
editor_options: 
  chunk_output_type: console
---

@@

## MCLM parameters

@@

## Parameters and representation in the original oblique space

@@

```{r item-plot-out}
#| fig.cap: |
#|   Item plots in an oblique test space, with original (i.e., standard)
#|   covariance matrix
plot_oblique + scale_color_manual(values = PALETTE)
```

@@

## Parameters and representation in oblique space with different variances

@@

```{r define-cov-matrix}
VARIANCES  <- c(2, 1.5)
sd_matrix  <- VARIANCES |> sqrt() |> diag()
cov_matrix <- sd_matrix %*% corr_matrix %*% sd_matrix
```

@@

```{r recompute-oblique-items}
# Oblique case:
